\documentclass[final,3p,times]{elsarticle}
%%\documentclass[final,5p,times,twocolumn]{elsarticle}
%%\documentclass[review,number,sort&compress]{elsarticle}
%%\documentclass[preprint,3p,times]{elsarticle}

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%% \usepackage{graphics}
%% or use the graphicx package for more complicated commands
\usepackage{setspace}
\usepackage{geometry}
\usepackage{lineno}
\usepackage{graphicx}
\usepackage{subfig}
%% or use the epsfig package if you prefer to use the old commands
%% \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amsmath}
\usepackage{amssymb}
%%\usepackage{animate}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}
%% \usepackage[compress]{natbib}

%% \journal{Nuclear Instruments and Methods in Physics Research A}

\begin{document}

Ms. Ref. No.:  NIMA-xxxxxxxx

Title: Characterization of Multianode Photomultiplier Tubes for use in the CLAS12 RICH Detector

Nuclear Inst. and Methods in Physics Research, A
\newline
\newline
\newline

To: Dr. Peter Krizan

Editor

Nuclear Inst. and Methods in Physics Research, A
\newline
\newline
\newline

Dear Dr. Krizan,
\newline

In the attached document please find our answers to the reviewers' comments.

We would like to use the opportunity to thank reviewers for their hard work of reading this difficult and extended paper, and highlighting parts requiring more detailed explanations and corrections. These findings justified some changes of the text. We believe addressing the comments from the reviewers helped us to improve the clarity of the paper. We tried to be as thorough as we could, but please tell if we did miss any important points.

The structure of the response document is based on the itemized reviewer's questions, followed by our comments and the corresponding changes in the text, if applicable, shown as the line comparison of the LaTeX texts before and after the correction. 

\newline

With my best regards,

Name xxxxxxxxxxxxxxxxxx
\newline

Address

phone\#xxxxxxx fax\#xxxxxxx  e-mail: xxxxxxx@jlab.org



\end{document}

\endinput
